Analyzing Security-Cost Trade-off for a \\ Fully Homomorphic Encryption Scheme

### 2013-06-16 Report/article.tex
g

\textbf{Sum of two unsigned integers of $32$ bits :} Sum of two $n$-bits sequences is performed using $n$ \texttt{full-adder} circuits (provided as \texttt{fhe\_fulladd(...)} function in the Scarab library). The cost of a full adder circuit is $2$ \texttt{XOR} to calculate the sum and $2$ \texttt{AND}, $1$ \texttt{XOR} and $1$ \texttt{OR} for the carry. Hence the total complexity is $3n$ \texttt{AND}, $5n$ \texttt{XOR}. \newline \newline

\textbf{Sum of two unsigned integers :} Sum of two $n$-bits sequences is performed using $n$ \texttt{full-adder} circuits (provided as \texttt{fhe\_fulladd(...)} function in the Scarab library). The cost of a full adder circuit is $2$ \texttt{XOR} to calculate the sum and $2$ \texttt{AND}, $1$ \texttt{XOR} and $1$ \texttt{OR} for the carry. Hence the total complexity is $3n$ \texttt{AND}, $5n$ \texttt{XOR}. \newline \newline

>>>>

\textbf{Sum of two unsigned integers of $32$ bits :} It is a sum of two $n$-bits sequences such as $n<32$ and it is performed using $n$ \texttt{full-adder} circuits (provided as \texttt{fhe\_fulladd(...)} function in the Scarab library). The cost of a full adder circuit is $2$ \texttt{XOR} to calculate the sum and $2$ \texttt{AND}, $1$ \texttt{XOR} and $1$ \texttt{OR} for the carry. Hence the total complexity is $3n$ \texttt{AND}, $5n$ \texttt{XOR}. \newline \newline

\textbf{Sum of two unsigned integers :} This program select the first $32$-bits sequences of the $2$ integers and does the sum of themexactly like the previous algorithm and then perform the sum with next $32$-bits sequences with the carry from the previous addition untill there is no sequence left.n in the Scarab library). So this program has approximately the same linear cost with the previous one \newline \newline
